Requirements analysis and specification 
In the following chapter, it will be described and rationale for software requirements analysis and specification. 
Users  needs
For the users needs, we use two method to get user’s needs or advices. For the first method, we used interview University of Bath international students. And we can get some ideas for our software. They tell us what is important or useful features on campus social networking for them. We think the interview is the most direct way to learn student’s needs. Another way is survey, survey is designed common social networking questions for university of bath. We can analysis survey’s result, and we can get a lot of different students’s needs. We put the survey on google form. And it has 26 result on it. Next we are going to detailed analysis interview result and survey result.

Interview detail
For this interview, we interview ten students. Nigh students are currently international University of Bath students. One student is pre University of Bath student. Each interview is about 5 minutes. And interview’s purpose is about campus social networking and international students studying. 
Below is our interviewer detail
Sun Haoxiang Msc computer science 1 year 
Q is our question. S: Sun Haoxiang
Q:how long are you on UK studying?
S: This is my first year on here.
Q:Ok, what is the biggest problem studying here?
S:I think language still is my problem. But i will try to solve it soon.
Q: what is best way to solve it?
S: i think the best way is to make new Uk student friend. and i should attend more campus activity.
Q: what is problem to make new friend or attend campus activity?
S:  i do not have more information about campus activity. Sometimes, i always missed it. And i only have some connection with classmates on class. We do not have much talking after class. i think this two biggest problem for me. 

Huang Zechun Undergraduate Mathematic 3 year 
Q is our question. H is Huang Zechun
Q: Hello, ZeChun, are you fresh student on here?
H: Yes, this is my first year on here. But i have 2 years on Uk high school.
Q: OK, what is different High school and University of Bath.
H: i think most thing is similar. But here is more freedom for me. And i think classmates is different for different lecture. this is big problem for me.
Q: why is different classmates on different lecture is problem for you?
H: Sometimes, i met studying problem is hard to find classmates to discuss.
Q: You can use University Moodle’s disuse page to do it. Why are you did not to use it ?
H: Moodle is more official. Most student and me do not like to use it. I see most students like to discuss on some social media (such as Facebook, skype). 
Q:Do you want to make new friend on class?
H: Yes, of course, i think it can help my studying. You know, make new friend is not easy thing for international student.  

